---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mturkr

<!-- badges: start -->
https://img.shields.io/badge/AndrewLi-mturkr-green
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://cran.r-project.org/web/licenses/MIT)
<!-- badges: end -->

The goal of `mturkr` is to easily and quickly create the the batch data set needed to send back to Amazon Mechanical Turk. This package will create a new data set with the required reject and approve columns to for participants payment.

I use MTurk a lot for my data collection so I think it is worthwhile to create a package of the functions I use a lot. I mainly intend to use this myself but if you use MTurk for data collection as well, you might find this package useful 

## Installation

You can install the development version of `mturkr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andr3wli/mturkr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mturkr)
```

